### 2022-05-31 article.tex
Remove paragraphs visible in text

\paragraph{Universities produce knowledge}

@@

\paragraph{A paper contains data and should be FAIR data}

@@

\paragraph{A paper is data and should be FAIR data}

@@

\paragraph{For some fields, the experiment is actually run by code}

@@

\paragraph{The experiments within genetic epidemology works are done by code}

@@

\paragraph{The code is the paradata for the results of an experiment}

@@

\paragraph{Science should be reproducible}

@@

\paragraph{Code should be published}

@@

\paragraph{Example of code being the ground truth}

@@

\paragraph{Raw code is important}

@@

\paragraph{Raw code is an indicator of quality}

@@

\paragraph{The problems with raw code}

@@

\paragraph{Raw code is already better than no code}

@@

\paragraph{Example of hosted code}

@@

\paragraph{Hosted code has important metadata}

@@

\paragraph{Hosted code has a commit history}

@@

\paragraph{A commit history helps assess honest reporting}

@@

\paragraph{Continuous integration helps assess code quality}

@@

\paragraph{Code coverage helps assess code quality}

@@

\paragraph{Metrics help assess the honest division of labour}

@@

\paragraph{A reader can contact the author}

@@

\paragraph{The problems with hosted code}

@@

\paragraph{Suggestions for knowledge management}

@@

\paragraph{Containers allow for runnable code, for longer periods of time}

@@

\paragraph{Runnable code can precisely reproduce an experiment}

@@

\paragraph{Runnable code allows others to re-use an experiment}

@@

\paragraph{The problems with runnable code}

@@

\paragraph{Runnable code is the pinnacle of reproducible research}

@@

\paragraph{Definition of paradata}

@@

\paragraph{The drawbacks of publishing code}

@@

\paragraph{The drawbacks of publishing version-controlled code}

@@

\paragraph{The drawbacks of publishing a running version of code}

@@

\paragraph{Still need the same data to do a reproducible experiment}

\paragraph{Recommendations}

@@

\paragraph{Final word}

>>>>

% \paragraph{Universities produce knowledge}

@@

% \paragraph{A paper contains data and should be FAIR data}

@@

% \paragraph{A paper is data and should be FAIR data}

@@

% \paragraph{For some fields, the experiment is actually run by code}

@@

% \paragraph{The experiments within genetic epidemology works are done by code}

@@

% \paragraph{The code is the paradata for the results of an experiment}

@@

% \paragraph{Science should be reproducible}

@@

% \paragraph{Code should be published}

@@

% \paragraph{Example of code being the ground truth}

@@

% \paragraph{Raw code is important}

@@

% \paragraph{Raw code is an indicator of quality}

@@

% \paragraph{The problems with raw code}

@@

% \paragraph{Raw code is already better than no code}

@@

% \paragraph{Example of hosted code}

@@

% \paragraph{Hosted code has important metadata}

@@

% \paragraph{Hosted code has a commit history}

@@

% \paragraph{A commit history helps assess honest reporting}

@@

% \paragraph{Continuous integration helps assess code quality}

@@

% \paragraph{Code coverage helps assess code quality}

@@

% \paragraph{Metrics help assess the honest division of labour}

@@

% \paragraph{A reader can contact the author}

@@

% \paragraph{The problems with hosted code}

@@

% \paragraph{Suggestions for knowledge management}

@@

% \paragraph{Containers allow for runnable code, for longer periods of time}

@@

% \paragraph{Runnable code can precisely reproduce an experiment}

@@

% \paragraph{Runnable code allows others to re-use an experiment}

@@

% \paragraph{The problems with runnable code}

@@

% \paragraph{Runnable code is the pinnacle of reproducible research}

@@

% \paragraph{Definition of paradata}

@@

% \paragraph{The drawbacks of publishing code}

@@

% \paragraph{The drawbacks of publishing version-controlled code}

@@

% \paragraph{The drawbacks of publishing a running version of code}

@@

% \paragraph{Still need the same data to do a reproducible experiment}

% \paragraph{Recommendations}

@@

% \paragraph{Final word}
